Ladies' figure skating in the 2002 Winter Olympics

### 2022-10-25 inst/f1points.Rmd
whitespace
more work on new parametrization

```{r,label=showanordertableandhead,echo=FALSE,print=FALSE}
library(hyper2,quietly=TRUE)
top <- 11
H2016 <- ordertable2supp(F1_table_2016[seq_len(top),])
H2017 <- ordertable2supp(F1_table_2017[seq_len(top),])
H2018 <- ordertable2supp(F1_table_2018[seq_len(top),])
H2019 <- ordertable2supp(F1_table_2019[seq_len(top),])
```

@@

```{r,label=combineallyearssetup,echo=FALSE,cache=TRUE}
H2016a <- hyper2(brackets(H2016),d=powers(H2016),pnames=sub("Hamilton","Hamilton_pre", pnames(H2016)))
H2017a <- hyper2(brackets(H2017),d=powers(H2017),pnames=sub("Hamilton","Hamilton_post",pnames(H2017)))
H2018a <- hyper2(brackets(H2018),d=powers(H2018),pnames=sub("Hamilton","Hamilton_post",pnames(H2018)))
H2019a <- hyper2(brackets(H2019),d=powers(H2019),pnames=sub("Hamilton","Hamilton_post",pnames(H2019)))
Ha <- H2016a
Ha <- combine(Ha,H2017a)
Ha <- combine(Ha,H2018a) 
Ha <- combine(Ha,H2019a)
ignorethis <- samep.test(Ha,c("Hamilton_pre","Hamilton_post"))
```

@@

```{r, label=calcpoints_real, echo=FALSE, cache=TRUE}
```{r, label=calcpoints_real, echo=FALSE, cache=TRUE}
p <- formula1_points_systems()[[1]]   # real points system
dp2016 <- ordertable2points(as.ordertable(F1_table_2016[seq_len(top),]),p)
dp2016 <- sort(dp2016,decreasing=TRUE)
dp2016[] <- seq_along(dp2016)
m2016 <- maxp(H2016)
m2016 <- sort(m2016,decreasing=TRUE)
m2016[] <- seq_along(m2016)

dp2017 <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp2017 <- sort(dp2017,decreasing=TRUE)
dp2017[] <- seq_along(dp2017)
m2017 <- maxp(H2017)
m2017 <- sort(m2017,decreasing=TRUE)
m2017[] <- seq_along(m2017)

dp2018 <- ordertable2points(as.ordertable(F1_table_2018[seq_len(top),]),p)
dp2018 <- sort(dp2018,decreasing=TRUE)
dp2018[] <- seq_along(dp2018)
m2018 <- maxp(H2018)
m2018 <- sort(m2018,decreasing=TRUE)
m2018[] <- seq_along(m2018)

dp2019 <- ordertable2points(as.ordertable(F1_table_2019[seq_len(top),]),p)
dp2019 <- sort(dp2019,decreasing=TRUE)
dp2019[] <- seq_along(dp2019)
m2019 <- maxp(H2019)
m2019 <- sort(m2019,decreasing=TRUE)
m2019[] <- seq_along(m2019)
```

@@

par(pty='s')        # square plot
ox <- dp2016
oy <- ordertrans(m2016,dp2016)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2016 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray',cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2017
oy <- ordertrans(m2017,dp2017)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray', cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2018
oy <- ordertrans(m2018,dp2018)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2018 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray', cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2019
oy <- ordertrans(m2019,dp2019)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2019 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray',cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

@@

par(pty='s')        # square plot
ox <- dp2016z
oy <- ordertrans(m2016,dp2016z)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2016 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray',cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2017z
oy <- ordertrans(m2017,dp2017z)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray', cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2018z
oy <- ordertrans(m2018,dp2018z)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2018 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray', cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2019z
oy <- ordertrans(m2019,dp2019z)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2019 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray',cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

>>>>

```{r,label=loadlibs,echo=FALSE,print=FALSE}
library("hyper2",quietly=TRUE)
library("magrittr",quietly=TRUE)
```

```{r,label=showanordertableandhead,echo=FALSE,print=FALSE,cache=TRUE}
top <- 11
H2016 <- ordertable2supp(F1_table_2016[seq_len(top),])
H2017 <- ordertable2supp(F1_table_2017[seq_len(top),])
H2018 <- ordertable2supp(F1_table_2018[seq_len(top),])
H2019 <- ordertable2supp(F1_table_2019[seq_len(top),])
```

@@

```{r,label=combineallyearssetup,echo=FALSE,cache=TRUE}
H2016a <- H2016 %>% psubs("Hamilton","Hamilton_pre")
H2017a <- H2017 %>% psubs("Hamilton","Hamilton_post")
H2018a <- H2018 %>% psubs("Hamilton","Hamilton_post")
H2019a <- H2019 %>% psubs("Hamilton","Hamilton_post")
Ha <-  H2016a + H2017a + H2018a + H2019a
```

Do a statistical test:

```{r,testhamprepost,cache=TRUE}
ignorethis <- samep.test(Ha,c("Hamilton_pre","Hamilton_post"))
ignorethis
```

Do another statistical test:

@@

```{r, label=calcpoints_real_2016, echo=FALSE, cache=TRUE}
p <- formula1_points_systems()[[1]]   # real points system
dp2016 <- ordertable2points(as.ordertable(F1_table_2016[seq_len(top),]),p)
dp2016 <- sort(dp2016,decreasing=TRUE)
dp2016[] <- seq_along(dp2016)
m2016 <- maxp(H2016)
m2016 <- sort(m2016,decreasing=TRUE)
m2016[] <- seq_along(m2016)
```

```{r, label=calcpoints_real_2017, echo=FALSE, cache=TRUE}
dp2017 <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp2017 <- sort(dp2017,decreasing=TRUE)
dp2017[] <- seq_along(dp2017)
m2017 <- maxp(H2017)
m2017 <- sort(m2017,decreasing=TRUE)
m2017[] <- seq_along(m2017)

```{r, label=calcpoints_real_2018, echo=FALSE, cache=TRUE}
dp2018 <- ordertable2points(as.ordertable(F1_table_2018[seq_len(top),]),p)
dp2018 <- sort(dp2018,decreasing=TRUE)
dp2018[] <- seq_along(dp2018)
m2018 <- maxp(H2018)
m2018 <- sort(m2018,decreasing=TRUE)
m2018[] <- seq_along(m2018)
```

```{r, label=calcpoints_real_2019, echo=FALSE, cache=TRUE}
dp2019 <- ordertable2points(as.ordertable(F1_table_2019[seq_len(top),]),p)
dp2019 <- sort(dp2019,decreasing=TRUE)
dp2019[] <- seq_along(dp2019)
m2019 <- maxp(H2019)
m2019 <- sort(m2019,decreasing=TRUE)
m2019[] <- seq_along(m2019)
```

@@

par(pty='s')        # square plot
ox <- dp2016

print("m2016")
dput(m2016)
print("dp2016")
dput(dp2016)

oy <- ordertrans(m2016,names(dp2016))
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2016 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray',cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2017
oy <- ordertrans(m2017,names(dp2017))
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray', cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2018
oy <- ordertrans(m2018,names(dp2018))
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2018 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray', cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2019
oy <- ordertrans(m2019,names(dp2019))
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2019 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray',cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

@@

par(pty='s')        # square plot
ox <- dp2016z
oy <- ordertrans(m2016,names(dp2016z))
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2016 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray',cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2017z
oy <- ordertrans(m2017,names(dp2017z))
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray', cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2018z
oy <- ordertrans(m2018,names(dp2018z))
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2018 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray', cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)

par(pty='s')        # square plot
ox <- dp2019z
oy <- ordertrans(m2019,names(dp2019z))
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="points order",ylab="likelihood order",main='2019 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray',cex=0.6) }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```
